---
title: "RISE Aim 2 - Enrollment"
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
author: "My Vu"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: simplex
  pdf_document:
    toc: yes
---
  
  <style>
  .list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: darkorchid;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message =  F)

library(readxl)
library(readr)
#library(tidyr)
library(dplyr)
#library(tidyverse)
library(ggplot2)
library(purrr)
library(stringr)
library(lme4)
library(ggforce)
library(corrplot)
library(Hmisc)
library(gtsummary)
library(scales)
library(kableExtra)
library(ggpubr)
library(EnvStats)
library(multcomp)

library(ggthemes)
library(PupillometryR)
library(openxlsx)

library(emmeans)
library(here)

## load source code
#devtools::source_gist("2a1bb0133ff568cbe28d", filename = "geom_flat_violin.R")
```

```{r all-files-loading, include=FALSE}
# ------------------------------------------------------------
# Load all R scripts from a folder
# ------------------------------------------------------------


r_files <- list.files(
  path = here("Aim2", "Aim2_Analysis"),
  pattern = "\\.R$",
  full.names = TRUE
)

invisible(lapply(r_files, source))
```

Total N of 119 in enrollment log with 8 screenfailed/rejected => N = 111

```{r id-file-loading}
id_merge <- read.csv(here("Aim2", "Aim2_data", "enrollment_data.csv")
)
```


```{r raw-data-loading}
raw_data <- read.csv(here("Aim2", "Aim2_Data", "raw_frame_data.csv"))
```


```{r icatcher-files-loading}
#imports annotated data from folder
icatcher_files <- list.files(path=here("Aim2", "Aim2_Data", "aim2_annotation"),
                                recursive=T,
                                #pattern="*test-trial*|*test-post*",
                                full.names=T)
icatcher_file_names<-icatcher_files

n=length(icatcher_files)
for(i in 1:n){
    icatcher_file_names[i]<-str_extract(icatcher_files[i], "[^/]+$")
  }

#create df called icatcher_output with relevant information from icatcher file name
icatcher_output<-data.frame(icatcher_files,icatcher_file_names,word(icatcher_file_names,1,sep="\\_"),word(icatcher_file_names,2,sep="\\_"))

#rename columns to match Stim_Order
icatcher_output<-rename(icatcher_output,frame_id=3,response_uuid=4)

#remove id in babysibs, in retest, and extra IDs in consent ()
icatcher_output <- icatcher_output
```

```{r stim-order}
Stim_Order<-raw_data[raw_data$key == "videoShown",]
#reduces to rows that contained "test"
Stim_Order<-Stim_Order[grep("test",Stim_Order$frame_id),]

Stim_Order <- Stim_Order %>% dplyr::select(response_uuid, child_hashed_id, frame_id, value)

#check for duplicates
Stim_Order %>% group_by(child_hashed_id, frame_id) %>% filter(n() > 1) %>% ungroup() %>% distinct(child_hashed_id)
```

```{r age}
Part_Age <- id_merge %>% dplyr::mutate(Age = factor(Age, levels = c(6, 12))) %>% dplyr::select(response_uuid, Age, cohort, Gender) %>% filter(response_uuid %in% icatcher_output$response_uuid)
```

# Demographics

```{r demographics, eval = T}
demo <- read.csv(
  here("Aim2", "Aim2_Data", "demographics.csv")
) %>% 
  mutate(demographic__annual_income2 = factor(demographic__annual_income2, levels = c( "< 50,000", "50,000 - 100,000","101,000 - 200,000", "> 200,000")))%>% 
  mutate(Region = factor(Region, levels = c("Northeast", "Midwest", "South", "West"))) %>% 
  mutate(demographic__education_level2 = factor(demographic__education_level2, levels = c("High school", "Associate (some college)",  "Bachelor/College", "Graduate and Professional"))) %>% 
  mutate(race = factor(race, levels = c("American Indian or Alaska Native", "Asian", "Black or African American", "Native Hawaiian or Other Pacific Islander","White", "More than one race")))

demo %>% merge(Part_Age) %>% dplyr::select(Age, Gender, race, Ethnicity, demographic__education_level2, demographic__annual_income2, Region)%>%
  tbl_summary(
    by = "Age",
    statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                          "{median} ({p25}, {p75})",
                                     "{min}, {max}"),
                     all_categorical() ~ "{n} ({p})"),
digits = list(all_continuous() ~ 1, all_categorical() ~ c(0, 1)),
missing_text = "(Missing)"
  ) %>% add_overall()

```

MAKE SURE TO REMOVE LONG VIDEOS and TRIM the extra frames

```{r video-timing}
video_time <- raw_data[grepl("test",raw_data$frame_id, ignore.case = T),]

options(digits.secs = 3)

video_time <- video_time %>%
  filter(key %in% c("eventType", "timestamp")) %>%
  tidyr::pivot_wider(
    names_from = key,
    values_from = value
  ) %>%
  dplyr::select(response_uuid, child_hashed_id, frame_id, event_number, eventType, timestamp) %>%
  tidyr::pivot_wider(
    names_from = eventType,
    values_from = timestamp
  ) %>%
  mutate(across(starts_with("exp-lookit"),
                ~ as.POSIXct(.x, format = "%Y-%m-%dT%H:%M:%OS", tz = "UTC")))

# pull the timestamps of startRecording, videoStarted, videoPaused from frame data

clean_df <- video_time %>% dplyr::select(1:3, `exp-lookit-video:startRecording`, `exp-lookit-video:videoStarted`, `exp-lookit-video:videoPaused`, `exp-lookit-video:trialCompleted`) %>%
  tidyr::pivot_longer(
    cols = starts_with("exp-lookit-video"),
    names_to = "event_type",
    values_to = "timestamp"
  ) %>%
  filter(!is.na(timestamp))%>%
  group_by(response_uuid, child_hashed_id, frame_id, event_type) %>%
  arrange(timestamp, .by_group = TRUE) %>%
  mutate(event_idx = row_number()) %>%
  ungroup()%>%
  mutate(
    event_type = if_else(
      event_idx == 1,
      event_type,
      paste0(event_type, "_", event_idx)
    )
  )%>%
  dplyr::select(response_uuid, child_hashed_id, frame_id, event_type, timestamp) %>%
  tidyr::pivot_wider(
    names_from = event_type,
    values_from = timestamp
  ) 

clean_df <- clean_df %>% 
  dplyr::select(1:3, `exp-lookit-video:startRecording`, `exp-lookit-video:videoStarted`,`exp-lookit-video:videoPaused`, `exp-lookit-video:videoStarted_2`,  `exp-lookit-video:videoPaused_2`, `exp-lookit-video:trialCompleted`)

# calculate the time (secs) between recording and started, and paused and restarted
df_diff <- clean_df %>%
  mutate(record_1ststart = (as.numeric(difftime(`exp-lookit-video:videoStarted`, `exp-lookit-video:startRecording`, units = "secs")))) 

```

```{r exclusions-video-quality-issues}
#videos that had video quality issues: glitching, frame repetition, or pixelation that need to be excluded

exclusion_df <- read.csv(here("Aim2", "Aim2_Data", "longvideo_with_timestamp_march2026.csv")) %>% dplyr::select(-1)

```


# Geometric Social 

Note on how outcome was derive:

1. Remove frames coded as "nobabyface", "noface", "none", or "away" 
2. Remove "left", "right" frames with confidence < 85%
3. Use "left" vs "right" to code "target" vs "non-target" depending on the task and version. Calculate % looking for each social side as:
 
    % looking =  (target) / (target + non-target)
    
    *left & right frames all need to have >= 85% confidence. A trial must have at least 33% usable data (i.e. left, right frames at 85% confidence) to be included.
    
```{r geosocial-stim-order}
GS<-Stim_Order %>% filter(grepl("GeoSocial", value))
#merges participant order with icatcher output
GS_icatcher <- merge(x=GS,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=F) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))

GS_icatcher <- GS_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove))
```

```{r geosocial-timestamps}

aim2_timestamps_final <- here("Aim2", "Aim2_Data", "aim2_timestamps_final_2.xlsx")

frame_ct_gs <- read_xlsx(
  aim2_timestamps_final,
  sheet = "GeoSocial"
)
frame_ct_gs <- frame_ct_gs %>%
  mutate(frame = map2(`Frame Start` , `Frame End`, seq)) %>%
  tidyr::unnest(frame) %>%
  mutate(Trial = str_extract(`Trial Number`, "\\d+")) %>%
  dplyr::select(frame, Position, Trial) %>% dplyr::rename(position = Position)


frame_ct_gs <- frame_ct_gs %>%
  mutate(position = case_when(
    position == "left"  ~ "right",
    position == "right" ~ "left",
    TRUE ~ position
  ))
```

```{r geosocial-results}
GS_results <- process_icatcher(GS_icatcher, 
                               frame_ct_gs, 
                               Part_Age, 
                               use_version = F)

write.csv(GS_results$trial_counts %>%
    merge(GS_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(GS_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)),  here("Aim2", "Aim2_Computed_Data", "geosocial_usableframe.csv"), row.names = FALSE)
```

## Data count

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 

```{r geosocial-data-count, fig.width=10}
GS_enrollment <- compute_gaze_metrics(
  GS_results,
  Part_Age,
  task_type = "dual",
  usable_threshold = 0.33,
  remove_fixations = TRUE,
  remove_extreme_target = TRUE,
  collapse_vpc_hh = FALSE,
  type_task = NULL,
  task_icatcher = NULL
)
```


```{r geosocial-table, fig.width=10}
make_flow_table(GS_results, GS_enrollment, Part_Age)
summarise_quality_v2(GS_results, Part_Age)
summarise_trials(GS_enrollment)
```


## Analysis

```{r geosocial-analysis}
tab_geo <- run_condition_model(
    data = GS_enrollment$metrics,
    condition_var = "Age",
    metric = "target_prop",
    chance_level = 0.5,
    random_effects = c(
      "(1 | response_uuid)",
      "(1 | Trial)"
    ),
    interaction = FALSE
)

output_path <- here("Aim2", "Aim2_Computed_Data", "geosocial.csv")

write.csv(
    GS_enrollment$metrics %>%
      dplyr::select(response_uuid, Age, Trial, target_prop),
    output_path,
    row.names = FALSE
  )
```

```{r geosocial-plot}

plot1_rise<- ggplot(data = GS_enrollment$metrics_avg, 
       mapping = aes(x = Age, 
                     y = target_prop_avg, 
                     fill = Age)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age", 
       y = "Proportion of looks fixating on\nsocial stimuli\n")+ stat_n_text(size = 4, y.pos = 0)  +scale_fill_manual(values=c("palevioletred2", "palevioletred3")) + theme_few() + geom_hline(yintercept=0.5, linetype="dashed", color = "red") + theme(text = element_text(size = 15))+ guides(fill="none") + scale_y_continuous(breaks = c(0, 0.25, .50, .75, 1), limits = c(-0.1, 1), labels = c("0.00", "0.25", "0.50", "0.75", "1.00"))

```    

# VPC
8 versions, participants sees both object & face stimuli

Note on how outcome was derive:

1. Remove frames coded as "nobabyface", "noface", "none", or "away" 
2. Remove frames with with confidence < 85%
3. Use "left" vs "right" to code "target" vs "non-target" depending on the task and version. Calculate % looking for each novel side as:
 
    % looking =  (target) / (target + non-target)
    
    *left & right frames all need to have >= 85% confidence. A trial must have at least 33% usable data (i.e. left, right frames at 85% confidence) to be included.
    
```{r vpc-stim-order}
vpc<-Stim_Order %>% filter(grepl("VPC", value))
vpc_icatcher <- merge(x=vpc,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=F) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))

vpc_icatcher <- vpc_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove)) %>% 
  mutate(value = gsub(".*/([^/]+)\\.webm$", "\\1", value)) %>%
  dplyr::mutate(value = gsub("_Aim2", "", value))

vpc_icatcher$Version<- vpc_icatcher$value

```

```{r vpc-timestamps}

labeled_frames_vpc <- read_xlsx(
  aim2_timestamps_final,
  sheet = "VPC"
)

labeled_frames_vpc <- labeled_frames_vpc %>%
  mutate(Position = str_extract(Position, "left|right"))

labeled_frames_vpc <- labeled_frames_vpc %>%
  mutate(Position = case_when(
    Position == "left"  ~ "right",
    Position == "right" ~ "left",
    TRUE ~ Position
  ))


# Step 2: expand frame ranges into one row per frame
labeled_frames_vpc <- labeled_frames_vpc %>%
  rowwise() %>%
  mutate(frame = list(seq(`Frame Start`, `Frame End`))) %>%
  tidyr::unnest(frame) %>%
  ungroup() %>%
  dplyr::select(frame, Trial = `Trial Number`, Version, Position)

# Step 3: pivot so each version becomes its own column
labeled_frames_vpc <- labeled_frames_vpc %>%
  tidyr::pivot_wider(
    names_from  = Version,
    values_from = Position
  )

```

```{r vpc-read-timstamps}
type_vpc <- read_xlsx(aim2_timestamps_final,sheet = "VPC") %>%
  dplyr::select(1:3)

```

```{r vpc-results}
vpc_results <- process_icatcher(vpc_icatcher, 
                                labeled_frames_vpc, 
                                Part_Age,
                                use_version = T)

write.csv(vpc_results$trial_counts %>%
    merge(vpc_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(vpc_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)),   here("Aim2", "Aim2_Computed_Data", "vpc_usableframe.csv"), row.names = FALSE)
```

## Data count

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 

```{r vpc-data-count, fig.width=10}
vpc_enrollment <- compute_gaze_metrics(
    vpc_results,
    Part_Age,
    task_type = c("dual"),
    usable_threshold = 0.33,
    remove_fixations = TRUE,
    remove_extreme_target = TRUE,
    collapse_vpc_hh = TRUE,
    type_task = type_vpc,
    task_icatcher = vpc_icatcher
)
```

```{r vpc-table, fig.width=10}
make_flow_table(vpc_results, vpc_enrollment, Part_Age)
summarise_quality_v2(vpc_results, Part_Age)
summarise_trials(vpc_enrollment)
```


## Analysis

```{r vpc-analysis}
output_path <- here("Aim2", "Aim2_Computed_Data", "vpc.csv")

write.csv(
    vpc_enrollment$metrics %>%
      dplyr::select(response_uuid, Age, `Trial Total`, target_prop, `Stimulus type`),
    output_path,
    row.names = FALSE
  )
```

```{r vpc-outcome-table}
tab_vpc <- run_condition_model(
    data = vpc_enrollment$metrics %>% dplyr::rename(Stimulus_type = "Stimulus type"),
    condition_var = c("Age", "Stimulus_type"),
    metric = "target_prop",
    chance_level = 0.5,
    random_effects = c(
      "(1 | response_uuid)",
      "(1 | `Trial Total`)"
    ),
    interaction = T
) %>% filter(!grepl("6 - 12", Condition))
```

effect of stimulus type overall, among 6 (Social - Non-social) and among 12-mos (Social - Non-social); p-values: 

```{r vpc-model-analysis}
mod <-lmerTest::lmer(
    formula = target_prop ~ Age*Stimulus_type + (1 | response_uuid) + (1 | `Trial Total`),
    data = vpc_enrollment$metrics %>% dplyr::rename(Stimulus_type = "Stimulus type"),
    REML = TRUE
  )
emmeans(mod, pairwise ~ Stimulus_type)$contrasts

emmeans(mod, pairwise ~ Stimulus_type | Age)$contrasts
```

```{r vpc-plot}
VP_fig <- vpc_enrollment$metrics %>%
  dplyr::group_by(response_uuid, `Stimulus type`) %>%
  dplyr::summarise(
    target_prop_avg = mean(target_prop, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    `Stimulus type` = dplyr::case_when(
      `Stimulus type` == "Non-social" ~ "Fribbles",
      `Stimulus type` == "Social" ~ "Faces"
    ),
    `Stimulus type` = factor(
      `Stimulus type`,
      levels = c("Faces", "Fribbles")
    )
  )%>% merge(Part_Age,all.x=TRUE)  %>% dplyr::mutate(Age = factor(Age, levels = c(6, 12)))

plot4_rise <- ggplot(data = VP_fig, 
       mapping = aes(x = Age, 
                     y = target_prop_avg, 
                     fill = Age)) + facet_wrap(~`Stimulus type`) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age",
       y = "Proportion of looks fixating on\nnovel images\n") + stat_n_text(size = 4, y.pos = -0.1)  +scale_fill_manual(values=c("lightpink1", "lightpink3")) + theme_few() + geom_hline(yintercept=0.5, linetype="dashed", color = "red") + theme(text = element_text(size = 15)) + guides(fill="none") + scale_y_continuous(breaks = c(0, 0.25, .50, .75, 1), limits = c(-0.1, 1), labels = c("0.00", "0.25", "0.50", "0.75", "1.00"))
```


# Prediction 
2 versions LthenR vs RthenL

Note on how outcome was derive:

1. Remove frames coded as "nobabyface", "noface", "none", or "away" 
2. Remove "left", "right" frames with confidence < 85%
3. Use "left" vs "right" to code "target" vs "non-target" depending on the task and version. For each test trials for each block (2-8) and (10-16), an AEM = if participant looks at target at all during critical window. 

For each block, compute total trials per participant, then calculate proportion of AEM trials as final outcome.

    
```{r prediciton-stim-order}
prediction<-Stim_Order %>% filter(grepl("Prediction", value))
prediction_icatcher <- merge(x=prediction,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=F) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))


prediction_icatcher <- prediction_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove)) %>% 
  mutate(value = gsub(".*/([^/]+)\\.webm$", "\\1", value))  %>% 
  dplyr::mutate(value = gsub("_Aim2", "", value))

prediction_icatcher$Version<- prediction_icatcher$value

```

```{r prediciton-timestamps}
labeled_frames_prediction <- read_xlsx(aim2_timestamps_final,
  sheet = "Prediction")

labeled_frames_prediction <- labeled_frames_prediction %>%
  mutate(frame = map2(`Frame Start` , `Frame End`, seq)) %>%
  tidyr::unnest(frame) %>%
  mutate(Trial = str_extract(`Trial Number`, "\\d+")) %>%
  dplyr::select(frame, contains("PredictionTarget"), Trial) 

labeled_frames_prediction <- labeled_frames_prediction %>%
  mutate(PredictionTargetLthenR = case_when(
    PredictionTargetLthenR == "left"  ~ "right",
    PredictionTargetLthenR == "right" ~ "left",
    TRUE ~ PredictionTargetLthenR
  ))

labeled_frames_prediction <- labeled_frames_prediction %>%
  mutate(PredictionTargetRthenL = case_when(
    PredictionTargetRthenL == "left"  ~ "right",
    PredictionTargetRthenL == "right" ~ "left",
    TRUE ~ PredictionTargetRthenL
  ))
```

```{r prediciton-results}
Prediction_results <- process_icatcher(
    prediction_icatcher,
    labeled_frames_prediction,
    Part_Age,
    use_version = T
)
  
write.csv(Prediction_results$trial_counts %>%
    merge(Prediction_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(prediction_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)), here("Aim2", "Aim2_Computed_Data", "prediction_usableframe.csv"), row.names = FALSE)
```


```{r prediction-enrollment-fig, fig.width=10}
Prediction_enrollment <- compute_gaze_metrics(
    Prediction_results,
    Part_Age,
    task_type = "dual",
    usable_threshold = 0.33,
    remove_fixations = FALSE,
    remove_extreme_target = FALSE,
    collapse_vpc_hh = FALSE,
    type_task = NULL,
    task_icatcher = NULL
)
```

## Data count

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 

```{r prediction-data-count, fig.width=10}
make_flow_table(Prediction_results, Prediction_enrollment, Part_Age)
summarise_quality_v2(Prediction_results, Part_Age)
```

Filter out trials 1 and 9. Participants must have at least 1 AEM trial in Block 2.
Must have usable data for at least 2 trials in block 1 for block 1 outcome to be included. Similarly for block 2.

```{r prediction-results}
# Filter out trials 1 and 9, then classify each trial as AEM or non-AEM
# based on whether target_prop > 0, and assign trials to Block 1 (trials 2-8)
# or Block 2 (remaining trials)

prediction_enr <- Prediction_enrollment$metrics %>% filter(!Trial %in% c("1","9")) %>%
  dplyr::mutate(aem = ifelse(target_prop > 0, "aem", "no aem")) %>% 
  dplyr::mutate(block = ifelse(Trial %in% as.character(2:8), "Block 1", "Block 2"))

# --- Block 2 Summary ---
df_b2 <- prediction_enr %>% 
  filter(block == "Block 2") %>%
  # Count AEM and non-AEM trials per participant
  dplyr::group_by(response_uuid, aem) %>% 
  dplyr::summarise(n = n()) %>% 
  ungroup() %>%
  # Ensure every participant has both AEM and non-AEM rows (fill missing with 0)
  tidyr::complete(response_uuid, aem) %>% 
  dplyr::mutate(n = ifelse(is.na(n), 0, n)) %>%
  # Compute total trials per participant, then calculate proportion of AEM trials
  dplyr::group_by(response_uuid) %>% 
  dplyr::mutate(n2 = sum(n)) %>% 
  filter(aem == "aem") %>% 
  dplyr::mutate(aem_prop = n / n2) %>% 
  # Merge in participant age information
  merge(Part_Age, all.x = T) %>%
  dplyr::mutate(block = "Block 2") %>%
  # Keep only participants who had at least 1 AEM trial in Block 2
  filter(n > 0)  

# --- Block 1 Summary ---
df_b1 <- prediction_enr %>% 
  filter(block == "Block 1") %>%
  # Count AEM and non-AEM trials per participant
  dplyr::group_by(response_uuid, aem) %>% 
  dplyr::summarise(n = n()) %>% 
  ungroup() %>%
  # Ensure every participant has both AEM and non-AEM rows (fill missing with 0)
  tidyr::complete(response_uuid, aem) %>% 
  dplyr::mutate(n = ifelse(is.na(n), 0, n)) %>%
  # Compute total trials per participant, then calculate proportion of AEM trials
  dplyr::group_by(response_uuid) %>% 
  dplyr::mutate(n2 = sum(n)) %>% 
  filter(aem == "aem") %>% 
  dplyr::mutate(aem_prop = n / n2) %>%
  # Merge in participant age information
  merge(Part_Age, all.x = T) %>%
  dplyr::mutate(block = "Block 1") %>%
  # Keep only participants who also appear in Block 2 (for matched comparison)
  filter(response_uuid %in% df_b2$response_uuid) 

prediction_final <- rbind(df_b1, df_b2) %>% 
  filter(n2 >= 2)
```

```{r prediction-final}
prediction_final %>% dplyr::select(1, Age, n2)  %>%
  dplyr::group_by(response_uuid)%>%
     summarise(n = sum(n2), Age = first(Age)) %>% dplyr::select(Age, n) %>%
    tbl_summary(
      by   = Age,
      type = list(n ~ "continuous2"),
      statistic = list(
        all_continuous()  ~ c("{median} ({p25}, {p75})", "{min}, {max}"),
        all_categorical() ~ "{n} / {N} ({p}%)"
      ),
      digits       = all_continuous() ~ 2,
      missing_text = "(Missing)"
    ) %>% modify_caption("**Median (IQR) number of test trials with usable data (final analytic)**")
```


```{r prediction-plot, fig.width= 12}
trial_by_trial <- prediction_enr %>%
  semi_join(prediction_final, by = c("response_uuid", "block")) %>% filter(Age == 6) %>%
  dplyr::group_by(Trial, aem)%>%
     summarise(n = n()) %>%
     mutate(freq = (n / sum(n))) %>% group_by(Trial) %>% mutate(n2 = sum(n)) %>% filter(aem == "aem")  %>% ungroup() %>% mutate(time = paste0(Trial, " \n(N = ", n2, ")")) %>% mutate(Trial = as.numeric(as.character(Trial))) %>% arrange(Trial) 

trial_by_trial <- trial_by_trial %>% rowwise()%>% mutate(p_val = prop.test(x = n, n = n2, alternative = "greater")[[3]]) %>% mutate(label_pp = paste0(round(freq,2))) %>% mutate(Color = ifelse(p_val < 0.05, "red", "black"))

checkpred <- prediction_enr %>%
  semi_join(prediction_final, by = c("response_uuid", "block")) %>% filter(Age == 6) 
length(unique(checkpred$response_uuid))

p1_aem <- trial_by_trial %>% ggplot(aes(x=Trial,
                           y=freq)) + theme_bw() +
 geom_point(aes(color = Color), size = 4) + geom_line() + scale_x_continuous(breaks=c(2:8, 10:16), labels= trial_by_trial$time) + ylab("Proportion of babies with an AEM to Target Side\n") + scale_y_continuous(breaks = c(0.0, .25, .50, .75, 1.0), limits = c(0, 1), labels = c(0.0, .25, .50, .75, 1.0))+ ggtitle("Age 6 (months)")+
      theme(
        #panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        title = element_text(size = 16)
        )+
  geom_text(aes(label = label_pp),
            size = 5, vjust = -1)  +
  scale_color_identity() 


trial_by_trial <- prediction_enr %>%
  semi_join(prediction_final, by = c("response_uuid", "block")) %>% filter(Age == 12) %>%
  dplyr::group_by(Trial, aem)%>%
     summarise(n = n()) %>%
     mutate(freq = (n / sum(n))) %>% group_by(Trial) %>% mutate(n2 = sum(n)) %>% filter(aem == "aem")  %>% ungroup() %>% mutate(time = paste0(Trial, " \n(N = ", n2, ")")) %>% mutate(Trial = as.numeric(as.character(Trial))) %>% arrange(Trial) 

trial_by_trial <- trial_by_trial %>% rowwise()%>% mutate(p_val = prop.test(x = n, n = n2, alternative = "greater")[[3]]) %>% mutate(label_pp = paste0(round(freq,2))) %>% mutate(Color = ifelse(p_val < 0.05, "red", "black"))

checkpred <- prediction_enr %>%
  semi_join(prediction_final, by = c("response_uuid", "block")) %>% filter(Age == 12) 
length(unique(checkpred$response_uuid))

p2_aem <- trial_by_trial %>% ggplot(aes(x=Trial,
                           y=freq)) + theme_bw() +
 geom_point(aes(color = Color), size = 4) + geom_line() + scale_x_continuous(breaks=c(2:8, 10:16), labels= trial_by_trial$time) + ylab("Proportion of babies with an AEM to Target Side\n") + scale_y_continuous(breaks = c(0.0, .25, .50, .75, 1.0), limits = c(0, 1), labels = c(0.0, .25, .50, .75, 1.0))+ ggtitle("Age 12 (months)")+
      theme(
        #panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        title = element_text(size = 16)
        )+
  geom_text(aes(label = label_pp),
            size = 5, vjust = -1)  +
  scale_color_identity() 
```

```{r predicition-output-fig, fig.height=12, fig.width=15}
ggarrange(p1_aem, p2_aem, ncol = 1, nrow = 2, labels = "auto")

p1_aem <- p1_aem +
  theme(
    axis.text.x = element_text(
      angle = 0,
      size = 10,    
      hjust = 0.5,
      vjust = 0.5
    ),
    axis.title.x = element_text(size = 14)
  )

p2_aem <- p2_aem +
  theme(
    axis.text.x = element_text(
      angle = 0,
      size = 10,
      hjust = 0.5,
      vjust = 0.5
    ),
    axis.title.x = element_text(size = 14)
  )

prediction_aem_fig <- ggarrange(
  p1_aem,
  p2_aem,
  ncol = 1,
  nrow = 2,
  labels = "auto",
  font.label = list(face = "bold", size = 10),
  hjust = -0.3
)

output_path <- here("Aim2", "Aim2_Computed_Data", "prediction.csv")

write.csv(
    prediction_final %>%
      dplyr::select(response_uuid, Age,block, aem_prop),
    output_path,
    row.names = FALSE
  )
```

Age 6 estimate is significant for being < 0.5 - so just a note. 

```{r prediction-table-results, eval = T}
tab_pred <- run_condition_model(
    data = prediction_final,
    condition_var = c("Age", "block"),
    metric = "aem_prop",
    chance_level = 0.5,
    random_effects =  c("(1 | response_uuid)"),
    interaction = T
)%>% filter(!grepl("6 - 12", Condition))
```

```{r prediction-plot2}

plot3_rise <- ggplot(data = prediction_final, 
       mapping = aes(x = Age, 
                     y = aem_prop, 
                     fill = Age)) + facet_wrap(~block) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age",
       y = "Proportion of AEMs to Target Side\n") + stat_n_text(size = 4, y.pos = -0.6)  +scale_fill_manual(values=c("lightsalmon1", "lightsalmon2")) + theme_few() + geom_hline(yintercept=0.5, linetype="dashed", color = "red") + theme(text = element_text(size = 15)) + guides(fill="none") 
```

# AV 

Note on how outcome was derive:

1. Remove frames coded as "nobabyface", "noface", "none", or "away" 
2. Remove "left", "right" frames  with confidence < 85%
3. Use "left" vs "right" to code "target" vs "non-target" depending on the task and version. Calculate % looking for each synch side as:
 
    % looking =  (target) / (target + non-target)
    
    *left & right frames all need to have >= 85% confidence. A trial must have at least 33% usable data (i.e. left, right frames at 85% confidence) to be included.
    
```{r av-stim-order}
AV<-Stim_Order %>% filter(grepl("AV", value))

AV_icatcher <- merge(x=AV,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=F) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))

AV_icatcher <- AV_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove))
```

```{r av-timestamps}
labeled_frames_av <- read_xlsx(aim2_timestamps_final, sheet = "AVSynch")

labeled_frames_av <- labeled_frames_av %>%
  mutate(frame = map2(`Frame Start` , `Frame End`, seq)) %>%
  tidyr::unnest(frame) %>%
  mutate(Trial = str_extract(`Trial Number`, "\\d+")) %>%
  dplyr::select(frame, Position, Trial) %>% dplyr::rename(position = Position)

labeled_frames_av <- labeled_frames_av %>%
  mutate(position = case_when(
    position == "left"  ~ "right",
    position == "right" ~ "left",
    TRUE ~ position
  ))
```

```{r av-results}
AV_results <- process_icatcher(AV_icatcher, 
                               labeled_frames_av, 
                               Part_Age, 
                               use_version = F)

write.csv(AV_results$trial_counts %>%
    merge(AV_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(AV_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)),   here("Aim2", "Aim2_Computed_Data", "av_usableframe.csv"), row.names = FALSE)

```

## Data count

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 

```{r av-data-count, fig.width=10}
AV_enrollment <- compute_gaze_metrics(
  AV_results,
  Part_Age,
  task_type = "dual",
  usable_threshold = 0.33,
  remove_fixations = TRUE,
  remove_extreme_target = TRUE,
  collapse_vpc_hh = FALSE,
  type_task = NULL,
  task_icatcher = NULL
)
```


```{r av-count-table, fig.width=10}
make_flow_table(AV_results, AV_enrollment, Part_Age)
summarise_quality_v2(AV_results, Part_Age)
summarise_trials(AV_enrollment)
```

## Analysis

```{r av-analysis-table}
tab_av <- run_condition_model(
    data = AV_enrollment$metrics,
    condition_var = "Age",
    metric = "target_prop",
    chance_level = 0.5,
    random_effects = c(
      "(1 | response_uuid)",
      "(1 | Trial)"
    ),
    interaction = FALSE
)


output_path <- here("Aim2", "Aim2_Computed_Data", "av.csv")
  
write.csv(
    AV_enrollment$metrics %>%
      dplyr::select(response_uuid, Age, Trial, target_prop),
    output_path,
    row.names = FALSE
  )
```

```{r av-plot}

plot2_rise<- ggplot(data = AV_enrollment$metrics_avg, 
       mapping = aes(x = Age, 
                     y = target_prop_avg, 
                     fill = Age)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age", 
       y = "Proportion of looks fixating on\nsynchronous stimuli\n")+ stat_n_text(size = 4, y.pos = 0)  +scale_fill_manual(values=c("lightgoldenrod1", "lightgoldenrod2")) + theme_few() + geom_hline(yintercept=0.5, linetype="dashed", color = "red") + theme(text = element_text(size = 15))+ guides(fill="none") + scale_y_continuous(breaks = c(0, 0.25, .50, .75, 1), limits = c(-0.1, 1), labels = c("0.00", "0.25", "0.50", "0.75", "1.00"))

```



# Word recognition

How outcome was derived:

Example of foot and milk (paired).
 
The word foot is the target in trial 1 and the distractor at trial 9.
the difference for foot = % looking at the word foot in trial 1 - % looking at the word foot in trial 9. Simplified:
 
foot_diff = trial1_target - trial9_distractor = trial1_target - (1 - trial9_target) = trial1_target + trial9_target - 1
 
But remember that the words are paired (these pairs are always shown together):
foot ~ milk
banana ~ hair
hand ~ yogurt
eyes ~ cookie
mouth ~ apple
 
The word milk then the target at trial 9 but the distractor at trial 1. So then for “milk”:
the difference for milk = % looking at the word milk in trial 9 - % looking at the word milk in trial 1. Simplified:
 
milk_diff = trial9_target – trial1_distractor = trial9_target - (1 - trial1_target) = trial9_target + trial1_target - 1
 
And then if you look at the math, foot_diff comes out to be the same as milk_diff (trial1_target + trial9_target – 1), so we just use this word-paired data once & we have 5 pairs in total. Kiddos will have up to 5 rows of final difference score.

The same thing repeats for trial 11 and trial 19.

Then the final data for foot ~ milk is: average %target - average %distractor = average of trial1_target & trial11_target - average of trial9_distractor & trial19_distractor. 


```{r word-rec-stim-order}
WL<-Stim_Order %>% filter(grepl("word", value))
WL_icatcher <- merge(x=WL,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=FALSE) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))

WL_icatcher <- WL_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove))
```

```{r word-rec-timestamps}
frame_ct_wl <- read_xlsx(aim2_timestamps_final, sheet = "WordRecognition_Timecourse")

frame_ct_wl <- frame_ct_wl %>% 
  dplyr::mutate(Image = tolower(Image)) %>%
  tidyr::separate(Image, c("Image #1", "Image #2"), sep = ",") %>%
  dplyr::mutate(`Image #2` = trimws(`Image #2`))

frame_ct_wl_fin <- frame_ct_wl  %>% dplyr::mutate(Audio = word(Audio,-1)) %>% 
   dplyr::mutate(patterns = map_chr(strsplit(`Image #1`, " "),paste,collapse="|"),
          match = ifelse(str_detect(Audio, patterns), `Image #1`, `Image #2`)) %>% 
   dplyr::select(-patterns) %>%
  dplyr::mutate(target.location = word(match,-1))

WL_pair_1 <- frame_ct_wl_fin %>% mutate(Trial = row_number()) %>% dplyr::select(Trial, `Image #1`, match) %>% dplyr::relocate(Trial, .before = `Image #1`) %>% filter(Trial %in% c(1:10)) 


for(word in unique(WL_pair_1$`Image #1`)){
  WL_pair_1 <- WL_pair_1 %>% dplyr::mutate(TargTrial = ifelse(match == `Image #1`, Trial, NA)) %>%
                              dplyr::mutate(DistTrial = ifelse(match != `Image #1`, Trial, NA))
}

WL_pair_1_1 <- WL_pair_1 %>%
  dplyr::group_by(`Image #1`) %>%
  tidyr::fill(everything(), .direction = "down") %>%
  tidyr::fill(everything(), .direction = "up") %>%dplyr::slice(1)%>% arrange(Trial)  %>% dplyr::rename(Variable = `Image #1`)

WL_pair_1 <- frame_ct_wl_fin %>% mutate(Trial = row_number()) %>% dplyr::select(Trial, `Image #2`, match) %>% dplyr::relocate(Trial, .before = `Image #2`) %>% filter(Trial %in% c(1:10)) 


for(word in unique(WL_pair_1$`Image #2`)){
  WL_pair_1 <- WL_pair_1 %>% dplyr::mutate(TargTrial = ifelse(match == `Image #2`, Trial, NA)) %>%
                              dplyr::mutate(DistTrial = ifelse(match != `Image #2`, Trial, NA))
}

WL_pair_1_2 <- WL_pair_1 %>%
  dplyr::group_by(`Image #2`) %>%
   tidyr::fill(everything(), .direction = "down") %>%
   tidyr::fill(everything(), .direction = "up") %>% filter(Trial %in% c(6:10))%>% arrange(Trial) %>% dplyr::rename(Variable = `Image #2`)

WL_pair_part1 <- rbind(WL_pair_1_1[,-3], WL_pair_1_2[,-3])


WL_pair_2 <-frame_ct_wl_fin %>% mutate(Trial = row_number()) %>% dplyr::select(Trial, `Image #1`, match) %>% dplyr::relocate(Trial, .before = `Image #1`) %>% filter(Trial %in% c(11:20)) 


for(word in unique(WL_pair_2$`Image #1`)){
  WL_pair_2 <- WL_pair_2 %>% dplyr::mutate(TargTrial = ifelse(match == `Image #1`, Trial, NA)) %>%
                              dplyr::mutate(DistTrial = ifelse(match != `Image #1`, Trial, NA))
}

WL_pair_2_1 <- WL_pair_2 %>%
  dplyr::group_by(`Image #1`) %>%
   tidyr::fill(everything(), .direction = "down") %>%
   tidyr::fill(everything(), .direction = "up") %>%dplyr::slice(1)%>% arrange(Trial) %>% dplyr::rename(Variable = `Image #1`)

WL_pair_2 <- frame_ct_wl_fin %>% mutate(Trial = row_number()) %>% dplyr::select(Trial, `Image #2`, match) %>% dplyr::relocate(Trial, .before = `Image #2`) %>% filter(Trial %in% c(11:20)) 


for(word in unique(WL_pair_2$`Image #2`)){
  WL_pair_2 <- WL_pair_2 %>% dplyr::mutate(TargTrial = ifelse(match == `Image #2`, Trial, NA)) %>%
                              dplyr::mutate(DistTrial = ifelse(match != `Image #2`, Trial, NA))
}

WL_pair_2_2 <- WL_pair_2 %>%
  dplyr::group_by(`Image #2`) %>%
   tidyr::fill(everything(), .direction = "down") %>%
   tidyr::fill(everything(), .direction = "up") %>% filter(Trial %in% c(16:20)) %>% arrange(Trial)  %>% dplyr::rename(Variable = `Image #2`)

WL_pair_part2 <- rbind(WL_pair_2_1[,-3], WL_pair_2_2[,-3])

WL_item.pairs <- rbind(WL_pair_part1,WL_pair_part2) %>% arrange(TargTrial) %>% dplyr::select(-Trial) 

```

```{r word-rec-labeling}
labeled_frames_WL <- frame_ct_wl_fin %>%
  mutate(frame = map2(`Frame Start` , `Frame End`, seq)) %>%
  tidyr::unnest(frame) %>%
  mutate(Trial = str_extract(`Trial Number`, "\\d+")) %>%
  dplyr::select(frame, target.location, Trial) 

#labeled_frames %>% group_by(Trial) %>% summarise(frame_start = min(frame), frame_end = max(frame)) %>% mutate(diff = frame_end - frame_start) %>% arrange(diff)


labeled_frames_WL <- labeled_frames_WL %>%
  mutate(target.location = case_when(
    target.location == "left"  ~ "right",
    target.location == "right" ~ "left",
    TRUE ~ target.location
  )) %>% dplyr::rename(position = target.location)


```

```{r word-rec-results}
WL_results <- process_icatcher(WL_icatcher, 
                               labeled_frames_WL, 
                               Part_Age,
                               use_version = F)

write.csv(WL_results$trial_counts %>%
    merge(WL_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(WL_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)),   here("Aim2", "Aim2_Computed_Data", "word_usableframe.csv"), row.names = FALSE)
```

## Timecourse graphs

```{r word-rec-timcourse, fig.width=15}
check_num <- WL_results$frame_level %>%
    mutate(target_num = case_when(
        look == "target"     ~ 1,
        look == "non_target" ~ 0,
        TRUE                 ~ NA_real_
    )) %>% merge(Part_Age, all.x = T) 

WL_item.pairs_1 <- WL_item.pairs
WL_item.pairs_1$Variable <- sub(" .*", "", WL_item.pairs_1$Variable)


time_course_age <- WL_results$frame_level %>%
  merge(Part_Age, all.x = T) %>%
  group_by(Trial, frame_within_trial, Age) %>%
  mutate(target_v1 = case_when(look == "target" ~ 1,
                               look == "non_target" ~ 0,
                               is.na(look) ~ NA_real_)) %>% 
  summarise(
    prop_target = mean(target_v1, na.rm = TRUE),
    n_infants   = sum(!is.na(target_v1)),
    .groups     = "drop"
  ) %>%
  mutate(Trial = factor(Trial, levels = sort(unique(as.numeric(Trial)))))

ggplot(time_course_age %>%
  mutate(
    Trial = paste0("Trial ", Trial),
    Trial = factor(Trial, levels = unique(Trial[order(as.numeric(gsub("Trial (\\d+).*", "\\1", Trial)))]))
  )%>%  mutate(ms_within_trial = (frame_within_trial - 1) * 33.3 + 367), aes(x = ms_within_trial, y = n_infants,
                             color = Age, fill = Age)) +
  #geom_line() +
  geom_smooth(method = "loess", span = 0.3, se = FALSE) +
  facet_wrap(~ Trial, nrow = 1) +
  labs(x = "\nMillisecond within trial (367ms after target word onset to last frame both objects visible)", y = "N infants with data",
       color = NULL, fill = NULL) +
  theme_classic(base_size = 12) +
 theme(
  legend.position = "top",
  strip.text      = element_text(size = 10),
  axis.text.x     = element_text(angle = 45, hjust = 1)
)  


# Define pair colors
pair_colors <- c(
    "foot ~ milk"    = "#E69F00",
    "banana ~ hair"  = "#56B4E9",
    "hand ~ yogurt"  = "#009E73",
    "eyes ~ cookie"  = "#CC79A7",
    "mouth ~ apple"  = "#D55E00"
)

# Prep data
plot_data <- time_course_age %>%
  merge(
    WL_item.pairs_1 %>%
      dplyr::select(1, 2) %>%
      dplyr::rename(Trial = TargTrial)
  ) %>%
  mutate(
    Word_Pair = case_when(
      Variable %in% c("foot",   "milk")   ~ "foot ~ milk",
      Variable %in% c("banana", "hair")   ~ "banana ~ hair",
      Variable %in% c("hand",   "yogurt") ~ "hand ~ yogurt",
      Variable %in% c("eyes",   "cookie") ~ "eyes ~ cookie",
      Variable %in% c("mouth",  "apple")  ~ "mouth ~ apple"
    ),
    Trial = paste0("Trial ", Trial, ": ", Variable),
    Trial = factor(
      Trial,
      levels = unique(Trial[order(as.numeric(gsub("Trial (\\d+):.*", "\\1", Trial)))])
    ),
    ms_within_trial = (frame_within_trial - 1) * 33.3 + 367
  ) %>%
  filter(n_infants >= 5)

# Plot
ggplot(plot_data,
       aes(x        = ms_within_trial,
           y        = prop_target,
           color    = Word_Pair,
           fill     = Word_Pair,
           linetype = Age)) +
  geom_line() +
  geom_smooth(method = "loess", span = 0.3, se = TRUE, alpha = 0.2) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  facet_wrap(~ Trial, nrow = 2) +
  scale_color_manual(values = pair_colors) +
  scale_fill_manual(values  = pair_colors) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  labs(
    x        = "\nMilliseconds within trial (367ms after target word onset)",
    y        = "Proportion of infants looking at target",
    color    = "Word Pair",
    fill     = "Word Pair",
    linetype = "Age (months)"
  ) +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "top",
    strip.text      = element_text(size = 10)
  )

```

```{r, eval=T}
ggplot(time_course_age %>% 
         mutate(ms_within_trial = (frame_within_trial - 1) * 33.3 + 367),
       aes(x = ms_within_trial, y = prop_target,
           color = Age, fill = Age)) +
  geom_point(size = 0.5, alpha = 0.3) + 
  geom_smooth(method = "loess", span = 0.3, se = TRUE, alpha = 0.2) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  labs(
    x     = "\nMillisecond  (367ms after target word onset to last frame both objects visible)",
    y     = "Proportion of infants looking at target",
    color = NULL,
    fill  = NULL,
    title = "Across all trials"
  ) +
  theme_classic(base_size = 12) +
  theme(legend.position = "top") + scale_x_continuous(breaks = seq(367, 3400, by = 200))
```


```{r timecourse-graphs}
# prep for the graphs

word_comp_timeseries_plot <- WL_results$frame_level %>%
  merge(Part_Age, all.x = TRUE) %>%
  mutate(
    propt = case_when(
      look == "target" ~ 1,
      look == "non_target" ~ 0,
      TRUE ~ NA_real_
    ),
    age_group = Age,
    age_group = factor(age_group, levels = c("6", "12")),
    t_onset = (frame_within_trial - 1) * 33.3 #kg note: this is for frame rate
  ) %>%
  filter(
    t_onset >= -1000,
    t_onset <= 3500,
    !is.na(propt),
    !is.na(age_group)
  )


word_comp_timecourse_by_age <- 
  ggplot(
    word_comp_timeseries_plot,
    aes(x = t_onset, y = propt, color = age_group, fill = age_group)
  ) +
  stat_smooth(geom = "errorbar", size = 0.3, alpha = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_vline(xintercept = c(0, 367, 3500), linetype = "dashed") +
  scale_x_continuous(
    breaks = c( 0, 367, 1000, 2000, 3500),
    limits = c(0, 3500)
  ) +
  scale_y_continuous(
    limits = c(0, 1)
  ) +
  scale_color_manual(
    name = "Age",
    values = c(
      "6" = "#2563EB",
      "12" = "#F59E0B"
    )
  ) +
  scale_fill_manual(
    name = "Age",
    values = c(
      "6" = "#2563EB",
      "12" = "#F59E0B"
    )
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 20),
    axis.text.x = element_text(size = 12),
    panel.spacing.x = unit(1.5, "lines")
  ) +
  labs(
    x = "Time since Target Word Onset",
    y = "Mean Proportion Target-Looking"
  ) +
  guides(
    color = guide_legend(
      override.aes = list(linewidth = 8)
    )
  )



word_comp_timecourse_by_age

```

```{r timecourse-graphs-by-pair}
# now by pair 

word_comp_timeseries_plot <- WL_results$frame_level %>%
  merge(Part_Age, all.x = TRUE) %>%
  mutate(
    propt = case_when(
      look == "target" ~ 1,
      look == "non_target" ~ 0,
      TRUE ~ NA_real_
    ),
    age_group = factor(as.character(Age), levels = c("6","12")),
    t_onset = (frame_within_trial - 1) * 33.3
  ) %>%
  merge(
    WL_item.pairs_1 %>%
      dplyr::select(Variable, TargTrial),
    by.x = "Trial",
    by.y = "TargTrial"
  ) %>%
  mutate(
    word_pair = case_when(
      Variable %in% c("foot","milk") ~ "foot ~ milk",
      Variable %in% c("banana","hair") ~ "banana ~ hair",
      Variable %in% c("hand","yogurt") ~ "hand ~ yogurt",
      Variable %in% c("eyes","cookie") ~ "eyes ~ cookie",
      Variable %in% c("mouth","apple") ~ "mouth ~ apple"
    )
  ) %>%
  filter(!is.na(propt))

word_comp_timecourse_by_pair <-
  ggplot(
    word_comp_timeseries_plot,
    aes(
      x = t_onset,
      y = propt,
      color = age_group,
      fill = age_group
    )
  ) +
  stat_smooth(
    geom = "errorbar",
    size = 0.3,
    alpha = 0.3
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_vline(xintercept = c(367, 3500), linetype = "dashed") +
  scale_x_continuous(
    breaks = c(0, 367, 1000, 2000, 3500),
    limits = c(0, 3500)
  ) +
  facet_wrap(
    ~ word_pair,
    ncol = 3
  ) +
  scale_color_manual(
    name = "Age",
    values = c(
      "6" = "#2563EB",
      "12" = "#F59E0B"
    )
  ) +
  scale_fill_manual(
    name = "Age",
    values = c(
      "6" = "#2563EB",
      "12" = "#F59E0B"
    )
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 20),
    axis.text.x = element_text(size = 12),
    panel.spacing.x = unit(1.5, "lines")
  ) +
  labs(
    x = "Time since Target Word Onset",
    y = "Mean Proportion Target-Looking"
  ) +
  guides(
    color = guide_legend(
      override.aes = list(linewidth = 8)
    )
  )
word_comp_timecourse_by_pair 

```

```{r timecourse-graphs-by-item, fig.width=10, fig.height=7, out.width='95%', fig.align='center'}

# by item
word_comp_timeseries_plot_item <- WL_results$frame_level %>%
  merge(Part_Age, all.x = TRUE) %>%
  mutate(
    propt = case_when(
      look == "target" ~ 1,
      look == "non_target" ~ 0,
      TRUE ~ NA_real_
    ),
    age_group = factor(as.character(Age), levels = c("6", "12")),
    t_onset = (frame_within_trial - 1) * 33.3
  ) %>%
  merge(
    WL_item.pairs_1 %>%
      dplyr::select(Variable, TargTrial),
    by.x = "Trial",
    by.y = "TargTrial"
  ) %>% mutate(
  Variable = factor(
    Variable,
    levels = c(
      "foot", "milk",
      "banana", "hair",
      "hand", "yogurt",
      "eyes", "cookie",
      "mouth", "apple"
    )
  )
)  %>%
  filter(
    !is.na(propt),
    !is.na(age_group),
    !is.na(Variable),
    t_onset >= 0,
    t_onset <= 3500
  )

word_comp_timecourse_by_item <-
  ggplot(
    word_comp_timeseries_plot_item,
    aes(
      x = t_onset,
      y = propt,
      color = age_group,
      fill = age_group
    )
  ) +
  stat_smooth(
    geom = "errorbar",
    size = 0.3,
    alpha = 0.3
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_vline(xintercept = c(367, 3500), linetype = "dashed") +
  scale_x_continuous(
    breaks = c(0, 367, 1000, 2000, 3500),
    limits = c(0, 3500)
  ) +
  scale_y_continuous(
    limits = c(0, 1)
  ) +
  facet_wrap(
    ~ Variable,
    ncol = 4
  ) +
  scale_color_manual(
    name = "Age",
    values = c(
      "6" = "#2563EB",
      "12" = "#F59E0B"
    )
  ) +
  scale_fill_manual(
    name = "Age",
    values = c(
      "6" = "#2563EB",
      "12" = "#F59E0B"
    )
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 10),
    strip.text = element_text(size = 12),
    panel.spacing.x = unit(1.2, "lines"),
    legend.position = "bottom"
  ) +
  labs(
    x = "Time since Target Word Onset",
    y = "Mean Proportion Target-Looking"
  ) +
  guides(
    color = guide_legend(
      override.aes = list(linewidth = 8)
    )
  )

word_comp_timecourse_by_item
```

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 

```{r word-rec-enrollment, fig.width=10}
WL_enrollment <- compute_gaze_metrics(
  WL_results,
  Part_Age,
  task_type = "dual",
  usable_threshold = 0.33,
  remove_fixations = TRUE,
  remove_extreme_target = TRUE,
  collapse_vpc_hh = FALSE,
  type_task = NULL,
  task_icatcher = NULL
)
```


```{r word-rec-table, fig.width=10}
make_flow_table(WL_results, WL_enrollment, Part_Age)
summarise_quality_v2(WL_results, Part_Age)
summarise_trials(WL_enrollment)
```


```{r word-rec-difference-score, eval = T}
diff <- c()

for(i in c(1:20)){
 diff[[i]] <- WL_enrollment$metrics %>% 
   filter(Trial %in% WL_item.pairs[i,2:3]) %>% 
   mutate(distract_good = 1-target_prop) %>% 
   dplyr::select(1,Trial, distract_good, target_prop) %>% 
   dplyr::mutate(percent = ifelse(Trial == as.character(i), target_prop, distract_good)) %>%
   dplyr::mutate(Trial = ifelse(Trial == as.character(i), "target", "distractor")) %>%
   dplyr::select(response_uuid, Trial, percent) %>% tidyr::spread(Trial, percent) 
}
```

```{r word-rec-list-count}
df_list_count <- bind_rows(diff, .id = "Trial") %>% merge(WL_item.pairs[,2:3] %>% dplyr::rename(Trial = TargTrial)) %>% filter(!is.na(distractor) & !is.na(target)) %>% merge(Part_Age,all.x=TRUE)
```

```{r word-rec-item-pairs}
WL_item.pairs$Variable <- sub(" .*", "", WL_item.pairs$Variable)

df_list_diff_enroll <- bind_rows(diff, .id = "Trial") %>% 
  merge(WL_item.pairs[,1:2] %>% dplyr::rename(Trial = TargTrial)) %>% 
  filter(!is.na(distractor) & !is.na(target)) %>% 
  tidyr::pivot_longer(cols = c(distractor, target), names_to = "location", values_to = "percent") %>% 
  dplyr::group_by(response_uuid, Variable, location) %>% 
  dplyr::summarise(percent_2 = mean(percent)) %>% 
  tidyr::spread(key = location, value = percent_2) %>% 
  dplyr::mutate(diff = target - distractor) %>% 
  dplyr::rename(Word = Variable)  %>% 
  merge(Part_Age,all.x=TRUE)  %>% dplyr::mutate(Age = factor(Age, levels = c(6,12)))

df_list_diff_enroll <- df_list_diff_enroll %>% ungroup() %>% dplyr::mutate(Word_Pair = case_when(Word %in% c("foot", "milk") ~ "foot ~ milk",
                                                                       Word %in% c("banana", "hair") ~ "banana ~ hair",
                                                                       Word %in% c("hand", "yogurt") ~ "hand ~ yogurt",
                                                                       Word %in% c("eyes", "cookie") ~ "eyes ~ cookie",
                                                                       Word %in% c("mouth", "apple") ~ "mouth ~ apple"))  %>%
  group_by(response_uuid, Word_Pair, Age, cohort) %>%
  dplyr::slice(1) %>%
  ungroup()

# c("foot (milk)", "hair (banana)", "hand (yogurt)", "cookie (eyes)", "mouth (apple)
```

Final word recognition N (lower due to % target or % distractor is not available for the "difference" calculation)

```{r word-rec-list-diff-enroll}
df_list_diff_enroll %>% distinct() %>%
  dplyr::group_by(response_uuid)%>%
     summarise(n = n(), Age = first(Age)) %>% ungroup()%>% dplyr::select(Age, n)%>%
    tbl_summary(
      by   = Age,
      type = list(n ~ "continuous2"),
      statistic = list(
        all_continuous()  ~ c("{median} ({p25}, {p75})", "{min}, {max}"),
        all_categorical() ~ "{n} / {N} ({p}%)"
      ),
      digits       = all_continuous() ~ 2,
      missing_text = "(Missing)"
    ) %>% modify_caption("**Median (IQR) number of test trials with usable data (final analytic)**")
```

```{r word-rec-output}
output_path <- here("Aim2", "Aim2_Computed_Data", "word_comp.csv")
  
write.csv(
    df_list_diff_enroll %>%
      dplyr::select(response_uuid, Age, Word_Pair,diff),
    output_path,
    row.names = FALSE
  )

tab_word <- run_condition_model(
    data = df_list_diff_enroll,
    condition_var = "Age",
    metric = "diff",
    chance_level = 0,
    random_effects = c(
        "(1 | response_uuid)",
        "(1 | Word_Pair)"
    ),
    interaction = FALSE
)

```

```{r word-rec-plot}
word_fig <- df_list_diff_enroll %>% dplyr::group_by(response_uuid) %>% dplyr::summarise(diff_good_avg = mean(diff)) %>% merge(Part_Age,all.x=TRUE)  %>% dplyr::select(response_uuid, Age, diff_good_avg)%>% dplyr::mutate(Age = factor(Age, levels = c(6, 12)))

plot5_rise <- ggplot(data = word_fig, 
       mapping = aes(x = Age, 
                     y = diff_good_avg, 
                     fill = Age)) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age",
       y = "Difference in proportions\n(target - distractor)\n") + stat_n_text(size = 4,y.pos = -0.7)  +scale_fill_manual(values=c("darkolivegreen2", "darkolivegreen3")) + theme_few() + geom_hline(yintercept=0, linetype="dashed", color = "red") + theme(text = element_text(size = 15)) + guides(fill="none") 

```

```{r word-rec-plot2}
word_fig_1 <- df_list_diff_enroll %>% dplyr::group_by(response_uuid) %>% dplyr::summarise(distractor_avg = mean(distractor), target_avg = mean(target)) %>% dplyr::select(response_uuid, distractor_avg, target_avg)

word_fig_long <- word_fig_1 %>%
  tidyr::pivot_longer(
    cols = c(distractor_avg, target_avg),
    names_to = "condition",
    values_to = "avg"
  ) %>%
  mutate(condition = recode(condition,
    "distractor_avg" = "Distractor",
    "target_avg" = "Target"
  ))

plot5_rise_2 <- ggplot(
  data = word_fig_long,
  mapping = aes(x = condition, y = avg, fill = condition)
) + 
  geom_flat_violin(
    scale = "count",
    trim = FALSE,
    position = position_nudge(x = 0.2)   # push violin to the right
  ) + 
  stat_summary(
    fun.data = mean_sdl,
    fun.args = list(mult = 1),
    geom = "pointrange",
    position = position_nudge(x = 0.2)
  ) + 
  geom_dotplot(
    binaxis = "y",
    binwidth = 0.05,
    stackdir = "center",
    method = "histodot",
    stackratio = 1,
    dotsize = 0.6
  ) + 
  scale_fill_manual(values = c(
    "Distractor" = "darkolivegreen3",
    "Target"     = "steelblue"
  )) +
  scale_y_continuous(
    limits = c(0, 1),
    breaks = seq(0, 1, by = 0.25)
  ) +
  labs(
    x = "",
    y = "Average proportion of looks\n fixating on the distractor vs the target"
  ) + 
  stat_n_text(size = 4, y.pos = 0) +
  theme_few() +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  theme(
    text = element_text(size = 15),
    legend.position = "none"
    # axis.text.x = element_blank(),
    # axis.ticks.x = element_blank()
  )
```

```{r word-rec-stats, eval = T}
df_list_diff <- bind_rows(diff, .id = "Trial") %>% 
  merge(WL_item.pairs[,1:2] %>% dplyr::rename(Trial = TargTrial)) %>% 
  filter(!is.na(distractor) & !is.na(target))%>% tidyr::pivot_longer(cols = c(distractor, target), names_to = "location", values_to = "percent") %>% merge(Part_Age,all.x=TRUE) 

stat_n_stuff <- df_list_diff %>% filter(Trial %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>% mutate(Age = factor(Age, levels = c("6", "12")))%>% mutate(Variable = factor(Variable, levels = c("foot" , "hair" , "hand" , "cookie", "mouth" ,"banana" ,"apple" ,"yogurt" ,"milk" , "eyes"))) %>% distinct(response_uuid, Trial,Variable, .keep_all = T)
  
word_bl_1 <- df_list_diff %>% filter(Trial %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>% mutate(Age = factor(Age, levels = c("6", "12")))%>% mutate(Variable = factor(Variable, levels = c("foot" , "hair" , "hand" , "cookie", "mouth" ,"banana", "apple" ,"yogurt" ,"milk" , "eyes")))  %>%  ggplot(aes(x = Variable, y = percent, fill = location)) + geom_boxplot(show.legend = T) +
    geom_jitter(color="black", size=0.1, alpha=0.9) + geom_hline(yintercept=0.5, linetype="dashed", color = "red") +scale_fill_manual(values=c("skyblue3", "skyblue4")) + theme_bw() +
    xlab("Age") + ylab("Proportion of looks at object when object is a target \nand when it is a distractor (%)")+ ggtitle("Block 1: Word comparisons") + stat_n_text(size = 3, data = stat_n_stuff)  + theme(text = element_text(size = 12), plot.title = element_text(size = 9)) + facet_wrap(vars(Age), nrow = 2, labeller = labeller(Age = 
    c("6" = "Age: 6 months",
      "12" = "Age: 12 months"))) + xlab("")  


df_list_diff <- bind_rows(diff, .id = "Trial") %>% 
  merge(WL_item.pairs[,1:2] %>% dplyr::rename(Trial = TargTrial)) %>% 
  filter(!is.na(distractor) & !is.na(target))%>% tidyr::pivot_longer(cols = c(distractor, target), names_to = "location", values_to = "percent") %>% merge(Part_Age,all.x=TRUE) 

stat_n_stuff <- df_list_diff %>% filter(!Trial %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>% mutate(Age = factor(Age, levels = c("6", "12")))%>% mutate(Variable = factor(Variable, levels = c("foot" , "hair" , "hand" , "cookie", "mouth" ,"banana", "apple" ,"yogurt" ,"milk" , "eyes")))  %>% distinct(response_uuid, Trial,Variable, .keep_all = T)
  
word_bl_2 <- df_list_diff %>% filter(!Trial %in% c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) %>% mutate(Age = factor(Age, levels = c("6", "12")))%>% mutate(Variable = factor(Variable, levels = c("foot" , "hair" , "hand" , "cookie", "mouth" ,"banana", "apple" ,"yogurt" ,"milk" , "eyes"))) %>%  ggplot(aes(x = Variable, y = percent, fill = location)) + geom_boxplot(show.legend = T) +
    geom_jitter(color="black", size=0.1, alpha=0.9) + geom_hline(yintercept=0.5, linetype="dashed", color = "red") +scale_fill_manual(values=c("skyblue3", "skyblue4")) + theme_bw() +
    xlab("Age") + ylab("Proportion of looks at object when object is a target \nand when it is a distractor (%)")+ ggtitle("Block 2: Word comparisons") + stat_n_text(size = 3, data = stat_n_stuff)  + theme(text = element_text(size = 12), plot.title = element_text(size = 9)) + facet_wrap(vars(Age), nrow = 2, labeller = labeller(Age = 
    c("6" = "Age: 6 months",
      "12" = "Age: 12 months"))) + xlab("")  
```

# Numeracy 

4 versions, participants sees ONLY small constant in 2 versions, and ONLY large constant in the other 2 versions.

Note on how outcome was derive:

1. Remove frames coded as "nobabyface", "noface", "none", or "away" 
2. Remove "left", "right" frames with confidence < 85%
3. Use "left" vs "right" to code "target" vs "non-target" depending on the task and version. Calculate % looking for each alternating/changing side as:
 
    % looking =  (target) / (target + non-target)
    
    *left & right frames all need to have >= 85% confidence. A trial must have at least 33% usable data (i.e. left, right frames at 85% confidence) to be included.

```{r numeracy-stim-order}
Numeracy<-Stim_Order %>% filter(grepl("Nume", value))

Numeracy_icatcher <- merge(x=Numeracy,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=FALSE) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))

Numeracy_icatcher <- Numeracy_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove))%>%
  mutate(value = gsub(".*/([^/]+)\\.webm$", "\\1", value))%>% 
  dplyr::mutate(value = gsub("_Aim2", "", value))


Numeracy_icatcher$Version<- Numeracy_icatcher$value
```

```{r numeracy-timestamps}
labeled_frames_numeracy <- read_xlsx(aim2_timestamps_final,
  sheet = "Numeracy")

labeled_frames_numeracy <- labeled_frames_numeracy %>%
  mutate(Position = str_extract(Position, "Left|Right"))

labeled_frames_numeracy <- labeled_frames_numeracy %>%
  mutate(Position = case_when(
    Position == "Left"  ~ "right",
    Position == "Right" ~ "left",
    TRUE ~ Position
  ))


# Step 2: expand frame ranges into one row per frame
labeled_frames_numeracy <- labeled_frames_numeracy %>%
  rowwise() %>%
  mutate(frame = list(seq(`Frame Start`, `Frame End`))) %>%
  tidyr::unnest(frame) %>%
  ungroup() %>%
  dplyr::select(frame, Trial = `Trial Number`, Version, Position)

# Step 3: pivot so each version becomes its own column
labeled_frames_numeracy <- labeled_frames_numeracy %>%
  tidyr::pivot_wider(
    names_from  = Version,
    values_from = Position
  )
```

```{r numeracy-results}
numeracy_results <- process_icatcher(Numeracy_icatcher, 
                                     labeled_frames_numeracy, 
                                     Part_Age, 
                                     use_version = T)

write.csv(numeracy_results$trial_counts %>%
    merge(numeracy_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(Numeracy_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)), here("Aim2", "Aim2_Computed_Data", "numeracy_usableframe.csv"), row.names = FALSE)
```

```{r numeracy-enrollment, fig.width=10}
numeracy_enrollment <- compute_gaze_metrics(
    numeracy_results,
    Part_Age,
    task_type = c("dual"),
    usable_threshold = 0.33,
    remove_fixations = TRUE,
    remove_extreme_target = TRUE,
    collapse_vpc_hh = FALSE,
    type_task = NULL,
    task_icatcher = NULL
)
```

## Data count

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 


```{r numeracy-data-count, fig.width=10}
make_flow_table(numeracy_results, numeracy_enrollment, Part_Age)
summarise_quality_v2(numeracy_results, Part_Age)
summarise_trials(numeracy_enrollment)
```

## Analysis

```{r numeracy-analysis}
type_num <- read_xlsx(
  aim2_timestamps_final,
  sheet = "Numeracy") %>%
  dplyr::select(2:3)

df_numeracy_enrollment <- numeracy_enrollment$metrics %>% 
  merge(Numeracy_icatcher %>% dplyr::select(1, Version)) %>% 
  merge(type_num %>% distinct()) %>%
  dplyr::mutate(`Stimulus type` = ifelse(grepl("Large", `Stimulus type`), "Large Constant", "Small Constant")) %>%
  dplyr::mutate(`Stimulus type` = factor(`Stimulus type`, 
                                        levels = c("Small Constant", "Large Constant")))
```

```{r numeracy-output}

output_path <- here("Aim2", "Aim2_Computed_Data", "numeracy.csv")
  
write.csv(
    df_numeracy_enrollment %>%
      dplyr::select(response_uuid, Age, Trial,target_prop, `Stimulus type`),
    output_path,
    row.names = FALSE
  )

tab_num <- run_condition_model(
    data = df_numeracy_enrollment %>% dplyr::rename(Stimulus_type = `Stimulus type`),
    condition_var = c("Age" ,"Stimulus_type"),
    metric = "target_prop",
    chance_level = 0.5,
    random_effects = c(
        "(1 | response_uuid)",
        "(1 | Trial)"
    ),
    interaction = T
)%>% filter(!grepl("6 - 12", Condition))


```

```{r numeracy-figure}

num_fig <- numeracy_enrollment$metrics_avg %>%
  merge(
    Numeracy_icatcher %>%
      dplyr::select(1, Version)
  ) %>%
  merge(
    type_num %>%
      dplyr::distinct()
  ) %>%
  dplyr::mutate(
    `Stimulus type` = dplyr::case_when(
      grepl("Large", `Stimulus type`) ~ "20-item constant stream",
      TRUE ~ "5-item constant stream"
    ),
    `Stimulus type` = factor(
      `Stimulus type`,
      levels = c(
        "5-item constant stream",
        "20-item constant stream"
      )
    )
  )

plot6_rise <- ggplot(data = num_fig, 
       mapping = aes(x = Age, 
                     y = target_prop_avg, 
                     fill = Age)) + facet_wrap(~`Stimulus type`) + 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age",
       y = "Proportion of looks fixating on\nalternating stimuli\n") + stat_n_text(size = 4, y.pos = -0.1)  +scale_fill_manual(values=c("mediumpurple1", "mediumpurple2")) + theme_few() + geom_hline(yintercept=0.5, linetype="dashed", color = "red") + theme(text = element_text(size = 15)) + guides(fill="none") + scale_y_continuous(breaks = c(0, 0.25, .50, .75, 1), limits = c(-0.1, 1), labels = c("0.00", "0.25", "0.50", "0.75", "1.00"))
```


# Helper Hinderer
8 versions, participants sees both helper and hinderer. 

Note on how outcome was derive:

1. Remove frames coded as "nobabyface", "noface", "none", or "away" 
2. Remove "left", "right" frames with confidence < 85%
2. Use "left" vs "right" to code "target" vs "non-target" depending on the task and version. Calculate % looking for each helper side as:
 
    % looking =  (target) / (target + non-target)
    
    *left & right frames all need to have >= 85% confidence. A trial must have at least 33% usable data (i.e. left, right frames at 85% confidence) to be included.

```{r hh-stim-order}
hh<-Stim_Order %>% filter(grepl("condition", value))

hh_icatcher <- merge(x=hh,y=icatcher_output, 
             by=c("response_uuid","frame_id"), all=FALSE) %>%
  anti_join(exclusion_df, by = c("response_uuid", "frame_id"))

hh_icatcher <- hh_icatcher %>% merge(df_diff) %>% mutate(
  frame_to_remove =
   round((record_1ststart * 1000) / 33.3)) %>% dplyr::select(1:6, frame_to_remove) %>% mutate(frame_to_remove = ifelse(is.na(frame_to_remove), 0, frame_to_remove))%>%
  mutate(value = gsub(".*/([^/]+)\\.webm$", "\\1", value))%>% 
  dplyr::mutate(value = gsub("_Aim2", "", value))


hh_icatcher$Version<- hh_icatcher$value

```

```{r hh-timestamps}
labeled_frames_hh <- read_xlsx(aim2_timestamps_final, sheet = "HelperHinderer")

labeled_frames_hh <- labeled_frames_hh %>%
  mutate(Position = str_extract(Position, "left|right"))

labeled_frames_hh <- labeled_frames_hh %>%
  mutate(Position = case_when(
    Position == "left"  ~ "right",
    Position == "right" ~ "left",
    TRUE ~ "habituation"
  ))


# Step 2: expand frame ranges into one row per frame
labeled_frames_hh <- labeled_frames_hh %>%
  rowwise() %>%
  mutate(frame = list(seq(`Frame Start`, `Frame End`))) %>%
  tidyr::unnest(frame) %>%
  ungroup() %>%
  dplyr::select(frame, Trial = `Trial Number`, Version, Position)

# Step 3: pivot so each version becomes its own column
labeled_frames_hh <- labeled_frames_hh %>%
  tidyr::pivot_wider(
    names_from  = Version,
    values_from = Position
  )
```

```{r hh-results}
hh_results <- process_icatcher(hh_icatcher, 
                                     labeled_frames_hh, 
                                     Part_Age, 
                                     use_version = T)

write.csv(hh_results$trial_counts %>%
    merge(hh_results$quality_flags %>% dplyr::select(-Age),
          by  = c("response_uuid", "Trial"),
          all = TRUE)%>%
    dplyr::mutate(
      has_icatcher  = ifelse(noicatcherdata != frames | is.na(noicatcherdata), T, F) 
    )%>%
    mutate(noicatcherdata = tidyr::replace_na(noicatcherdata, 0),
           n_icatcher     = frames - noicatcherdata) %>%
    dplyr::mutate(
      `Usable frames (%)` = round(count_85_non_na / frames,3)) %>% 
  dplyr::select(response_uuid, Trial, `Usable frames (%)`, has_icatcher) %>% merge(hh_icatcher %>% dplyr::select(response_uuid, icatcher_file_names)),   here("Aim2", "Aim2_Computed_Data", "hh_usableframe.csv"), row.names = FALSE)
```

```{r hh-enrollment, fig.width=10}
# look at the test trials only
hh_enrollment <- compute_gaze_metrics(
    hh_results,
    Part_Age,
    task_type = c("dual"),
    usable_threshold = 0.33,
    remove_fixations = TRUE,
    remove_extreme_target = TRUE,
    collapse_vpc_hh = FALSE,
    type_task = NULL,
    task_icatcher = NULL,
    trial_filter = c("7", "14")
)
```

## Data count

Number (and percent) of infants who viewed the task at all (2nd column, as % of consented sample with any icatcher data & in frame data , with sufficient usable data (3rd column, as % of infants who viewed the task),  with fixation on a single side >80% of the task (4th column, as % of infants with usable data), and final N in the analytic dataset. 


```{r hh-data-count, fig.width=10}
make_flow_table(hh_results, hh_enrollment, Part_Age)
summarise_quality_v2(hh_results, Part_Age)
summarise_trials(hh_enrollment)
```

For each block, a participant was required to have at least one usable helper trial and at least one hinderer trial (Block 1: trials 1–6; Block 2: trials 8–13), where usable trials were defined as having at least 33% of frames with valid iCatcher+ detections at ≥85% confidence.

```{r hh-includes}
data_include <- hh_results$trial_counts %>%
  dplyr::mutate(
    `Usable frames (%)` = round(count_85_non_na / frames, 3),
  ) %>%
  merge(Part_Age, all.x = TRUE) %>%
  filter(`Usable frames (%)` >= 0.33) %>%
  filter(!Trial %in% c("7", "14")) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(response_uuid) %>%
  mutate(
    include_block1 = any(Trial[Trial %in% 1:6] %% 2 == 1) &
                     any(Trial[Trial %in% 1:6] %% 2 == 0),
    include_block2 = any(Trial[Trial %in% 8:13] %% 2 == 1) &
                     any(Trial[Trial %in% 8:13] %% 2 == 0)
  ) %>%
  ungroup() %>%
  dplyr::select(response_uuid, include_block1, include_block2) %>%
  distinct()

df_hh <- hh_enrollment$metrics %>% merge(data_include) %>%
  filter(
    (Trial == 7  & include_block1) |
    (Trial == 14 & include_block2)
  ) 
```

```{r hh-distinct}
df_hh %>% distinct() %>%
  dplyr::group_by(response_uuid)%>%
     summarise(n = n(), Age = first(Age)) %>% ungroup()%>% dplyr::select(Age, n)%>%
    tbl_summary(
      by   = Age,
      type = list(n ~ "continuous2"),
      statistic = list(
        all_continuous()  ~ c("{median} ({p25}, {p75})", "{min}, {max}"),
        all_categorical() ~ "{n} / {N} ({p}%)"
      ),
      digits       = all_continuous() ~ 2,
      missing_text = "(Missing)"
    ) %>% modify_caption("**Median (IQR) number of test trials with usable data (final analytic)**")
```

## Analysis

```{r hh-output-path}
output_path <- here("Aim2", "Aim2_Computed_Data", "hh.csv")

write.csv(
    df_hh %>%
      dplyr::select(response_uuid, Age, Trial,target_prop),
    output_path,
    row.names = FALSE
  )

tab_hh <- run_condition_model(
    data = df_hh,
    condition_var = "Age",
    metric = "target_prop",
    chance_level = 0.5,
    random_effects = c(
        "(1 | response_uuid)"
    ),
    interaction = FALSE
)
```


```{r hh-plot}

hh_fig <- df_hh %>% dplyr::group_by(response_uuid) %>% dplyr::summarise(helper_good_avg = mean(target_prop)) %>% merge(Part_Age,all.x=TRUE)  %>% dplyr::select(response_uuid, Age, helper_good_avg)%>% dplyr::mutate(Age = factor(Age, levels = c(6, 12)))

plot7_rise <- ggplot(data = hh_fig, 
       mapping = aes(x = Age, 
                     y = helper_good_avg, 
                     fill = Age))+ 
  geom_flat_violin(scale = "count", 
                   trim = FALSE) + 
  stat_summary(fun.data = mean_sdl, 
               fun.args = list(mult = 1), 
               geom = "pointrange", 
               position = position_nudge(0.05)) + 
  geom_dotplot(binaxis = "y", 
               dotsize = 0.6, 
               stackdir = "down", 
               #binwidth = 0.1, 
               position = position_nudge(-0.025)) + 
  theme(legend.position = "none") + 
  labs(x = "Age",
       y = "Proportion of looks fixating on\nhelper stimuli\n") + stat_n_text(size = 4, y.pos = -0.1)  +scale_fill_manual(values=c("lightblue1", "lightblue2")) + theme_few() + geom_hline(yintercept=0.5, linetype="dashed", color = "red") + theme(text = element_text(size = 15)) + guides(fill="none") + scale_y_continuous(breaks = c(0, 0.25, .50, .75, 1), limits = c(-0.1, 1), labels = c("0.00", "0.25", "0.50", "0.75", "1.00"))
```

# Figures 

```{r show-plots, fig.height= 5, eval = T}
plot1_rise
plot3_rise
plot5_rise
plot2_rise
plot4_rise
plot6_rise
plot7_rise
```

```{r arrange-plots, fig.width= 12, fig.height=10}
ggarrange(word_bl_1,word_bl_2, ncol = 1, nrow = 2, labels = "auto", align= "hv", common.legend = T)
```


```{r usable-frames}
usableframes <- list.files(
   here("Aim2", "Aim2_Computed_Data"),
  full.names = TRUE,
  pattern = "_usable"
) %>%
  lapply(function(x) {
    read.csv(x) %>%
      mutate(Trial = as.character(Trial))
  })

tot_usable <- bind_rows(usableframes) 

tcatcher_processed <- icatcher_output %>% dplyr::select(response_uuid, icatcher_file_names, frame_id) %>% arrange(response_uuid, frame_id) %>% 
  merge(Stim_Order[,c(1,3,4)])  %>% 
  mutate(value = gsub(".*/([^/]+)\\.webm$", "\\1", value))

tot_usable  <- tot_usable %>% merge(tcatcher_processed)  %>% dplyr::select(response_uuid, frame_id, value, Usable.frames...., has_icatcher) %>% merge(Part_Age)
  

tot_usable <- tot_usable %>% mutate(value = case_when(grepl("Geo", value) ~ "Geo-Social Attention",
                                        grepl("AV", value) ~ "Audiovisual Synchrony",
                                        grepl("VPC", value) ~ "Visual Paired Comparison",
                                        grepl("word", value) ~ "Word Recognition",
                                        grepl("Pred", value) ~ "Prediction",
                                        grepl("Num", value) ~ "Numeracy",
                                        grepl("condi", value) ~ "Social Evaluation")) %>%
  dplyr::rename(task = value) %>% 
  dplyr::mutate(task_order = case_when(
    str_detect(frame_id, "trial") ~ as.numeric(str_extract(frame_id, "\\d+$")),
    str_detect(frame_id, "post")  ~ case_when(
      str_extract(frame_id, "\\d+$") == "1" ~ 6,
      str_extract(frame_id, "\\d+$") == "2" ~ 7
    )
  )) %>% arrange(response_uuid, task_order)

```

```{r usable-frames-overall, eval = T, fig.width= 15, fig.height=5}
# Per-task usable frame summary (excluding missing iCatcher trials)
task_usable <- tot_usable %>% dplyr::rename(usable_pct = Usable.frames....)%>%
  filter(has_icatcher) %>%                            # exclude missing iCatcher trials
  group_by(response_uuid, task) %>%
  summarise(
    task_order = first(task_order),
    avg_usable_pct   = mean(usable_pct, na.rm = TRUE),  # avg over reached trials only
    n_trials_reached = n(),                              # how many trials they reached
    .groups = "drop"
  ) %>%
  merge(Part_Age, all.x = TRUE) %>%
  mutate(
    task = factor(task, levels = c(                      # order by presentation
      "Geo-Social Attention",
      "Visual Paired Comparison",
      "Prediction",
      "Audiovisual Synchrony",
      "Word Recognition",
      "Numeracy",
      "Social Evaluation"
    ))
  )


# Separate completion rate summary
task_completion <- tot_usable %>% dplyr::rename(usable_pct = Usable.frames....) %>%
  group_by(response_uuid, task) %>%
  summarise(
    n_reached = sum(has_icatcher),  # trials iCatcher ran
    n_total   = n(),                                          # total expected trials
    completion_pct = n_reached / n_total * 100,
    .groups = "drop"
  ) %>%
  merge(Part_Age, all.x = TRUE)

# Plot 1: Attention quality (usable frames %)
p_vals <- task_usable %>%
  group_by(task) %>%
  summarise(
    p = wilcox.test(avg_usable_pct ~ Age)$p.value,
    .groups = "drop"
  ) %>%
  mutate(
    p_label = paste0("p = ", sprintf("%.3f", p)),
    y = 105
  ) %>%
  mutate(
    p_label = ifelse(p_label == "p = 0.000", "p < 0.001", p_label),
    y = 105
  )

n_labels <- task_usable %>%
  group_by(task, Age) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(label = paste0("n = ", n))

# Then replace stat_compare_means with:

usable_frames_plot <- ggplot(task_usable, aes(x = Age, y = avg_usable_pct * 100, fill = Age)) +
  geom_boxplot(width = 0.6, outlier.shape = NA, alpha = 0.7) +
  geom_jitter(aes(color = Age), width = 0.15, alpha = 0.5, size = 1.5) +
  geom_text(
    data = p_vals,
    aes(x = 1.5, y = 108, label = p_label),
    inherit.aes = FALSE,
    size = 4
  ) +
  geom_text(
    data = n_labels,
    aes(x = Age, y = -2, label = label),
    inherit.aes = FALSE,
    size = 4
  ) +
  facet_wrap(~ task, nrow = 1) +
  scale_y_continuous(limits = c(-6, 112), labels = function(x) paste0(x, "%")) +
  scale_fill_manual(values = c("6" = "grey70", "12" = "grey30")) +
  scale_color_manual(values = c("6" = "grey70", "12" = "grey30")) +
  labs(
    x     = NULL,
    y     = "Average % usable frames",
    fill  = NULL,
    color = NULL
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "none",
    panel.spacing   = unit(0.5, "lines")
  )
usable_frames_plot 
# task_completion %>%
#   mutate(high_completion = completion_pct == 0) %>%
#   group_by(task, Age) %>%
#   dplyr::summarise(
#     n    = sum(high_completion),
#     N    = n(),
#     pct  = mean(high_completion) * 100,
#     .groups = "drop"
#   ) %>%
#   mutate(cell = sprintf("%d (%.1f%%)", n, pct)) %>%
#   dplyr::select(task, Age, cell) %>%
#   tidyr::pivot_wider(names_from = Age, values_from = cell) 
```



```{r figure-usable-data, eval = T}
taskfin_1_6 <- task_usable  %>% 
  filter(Age == 6) %>% 
  filter(!task_order %in%  c(6,7)) %>% 
  mutate(task_order = factor(task_order)) %>%  
  ggplot(aes(x = task_order, y = avg_usable_pct * 100)) + 
  geom_boxplot(show.legend = T) +
  geom_jitter(color="black", size=0.3, alpha=0.9) + 
  #geom_hline(yintercept=33, linetype="dashed", color = "red") + 
  theme_bw() +
  xlab("Task order") + ylab("Average % usable frames")+ ggtitle("Age: 6 months") + stat_n_text(size = 4)  + 
  theme(text = element_text(size = 15), plot.title = element_text(size = 15)) + facet_wrap(vars(task), nrow = 2)+ stat_compare_means(
 aes(label = paste0("p = ", after_stat(p.format))),label.x = 3, label.y = 120, color = "red", size = 4) + ylim(-15, 150)

taskfin_2_6 <- task_usable  %>% 
  filter(Age == 6) %>% 
  filter(task_order %in%  c(6,7)) %>% 
  mutate(task_order = factor(task_order)) %>%  
  ggplot(aes(x = task_order, y = avg_usable_pct * 100)) + 
  geom_boxplot(show.legend = T) +
  geom_jitter(color="black", size=0.3, alpha=0.9) + 
  #geom_hline(yintercept=33, linetype="dashed", color = "red") + 
  theme_bw() +
    xlab("Task order") + ylab("Average % usable frames")+ ggtitle("Age: 6 months") + stat_n_text(size = 4)  + 
  theme(text = element_text(size = 15), plot.title = element_text(size = 15)) + facet_wrap(vars(task), nrow = 1)+ stat_compare_means(
 aes(label = paste0("p = ", after_stat(p.format))),label.x = 1.5, label.y = 100, color = "red", size = 4) + ylim(-10, 100)


taskfin_1_12 <- task_usable  %>% 
  filter(Age == 12) %>% 
  filter(!task_order %in%  c(6,7)) %>% 
  mutate(task_order = factor(task_order)) %>%  
  ggplot(aes(x = task_order, y = avg_usable_pct * 100)) + 
  geom_boxplot(show.legend = T) +
  geom_jitter(color="black", size=0.3, alpha=0.9) + 
  #geom_hline(yintercept=33, linetype="dashed", color = "red") + 
  theme_bw() +
    xlab("Task order") + ylab("Average % usable frames")+ ggtitle("Age: 12 months") + stat_n_text(size = 4)  + 
  theme(text = element_text(size = 15), plot.title = element_text(size = 15)) + facet_wrap(vars(task), nrow = 2)+ stat_compare_means(
 aes(label = paste0("p = ", after_stat(p.format))),label.x = 3, label.y = 120, color = "red", size = 4) + ylim(-15, 150)

taskfin_2_12 <- task_usable  %>% 
  filter(Age == 12) %>% 
  filter(task_order %in%  c(6,7)) %>% 
  mutate(task_order = factor(task_order)) %>%  
  ggplot(aes(x = task_order, y = avg_usable_pct * 100)) + 
  geom_boxplot(show.legend = T) +
  geom_jitter(color="black", size=0.3, alpha=0.9) + 
  #geom_hline(yintercept=33, linetype="dashed", color = "red") + 
  theme_bw() +
    xlab("Task order") + ylab("Average % usable frames")+ ggtitle("Age: 12 months") + stat_n_text(size = 4)  + 
  theme(text = element_text(size = 15), plot.title = element_text(size = 15)) + facet_wrap(vars(task), nrow = 1)+ stat_compare_means(
 aes(label = paste0("p = ", after_stat(p.format))),label.x = 1.5, label.y = 100, color = "red", size = 4) + ylim(-10, 100)

```

```{r arrange-figs2, fig.width= 12, fig.height=10, eval=T}
ggarrange(taskfin_1_6,taskfin_1_12, ncol = 1, nrow = 2, labels = "auto", align= "hv", common.legend = T)
```

```{r arrange-figs3, fig.width= 12, eval = T}
ggarrange(taskfin_2_6,taskfin_2_12, ncol = 2, nrow = 1, labels = "auto", align= "hv", common.legend = T)
```

# Final Tables 

```{r final-tables}
# ------------------------------------------------------------------------------
# Build Table 3
# ------------------------------------------------------------------------------
GS_quality_tbl         <- summarise_quality_v2(GS_results,        Part_Age)
vpc_quality_tbl        <- summarise_quality_v2(vpc_results,        Part_Age)
prediction_quality_tbl <- summarise_quality_v2(Prediction_results, Part_Age)
AV_quality_tbl         <- summarise_quality_v2(AV_results, Part_Age)
WL_quality_tbl         <- summarise_quality_v2(WL_results,         Part_Age)
numeracy_quality_tbl   <- summarise_quality_v2(numeracy_results,   Part_Age)
hh_quality_tbl         <- summarise_quality_v2(hh_results,         Part_Age)

age_levels <- sort(unique(Part_Age$Age))  # e.g. c("6mo", "12mo")

table3 <- bind_rows(
  compute_table3_row(GS_results,         GS_icatcher,         "Geo-Social Attention",               10, Part_Age, show_away = TRUE,  quality_tbl = GS_quality_tbl),
  compute_table3_row(vpc_results,        vpc_icatcher,        "Visual Paired Comparison (VPC)",      12, Part_Age, show_away = TRUE,  quality_tbl = vpc_quality_tbl),
  compute_table3_row(Prediction_results, prediction_icatcher, "Prediction",                          16, Part_Age, show_away = TRUE,  quality_tbl = prediction_quality_tbl),
  compute_table3_row(AV_results,         AV_icatcher,         "Audiovisual Synchrony",                6, Part_Age, show_away = TRUE,  quality_tbl = AV_quality_tbl),
  compute_table3_row(WL_results,         WL_icatcher,         "Word Comprehension",                  20, Part_Age, show_away = TRUE,  quality_tbl = WL_quality_tbl),
  compute_table3_row(numeracy_results,   Numeracy_icatcher,   "Numeracy",                             4, Part_Age, show_away = TRUE,  quality_tbl = numeracy_quality_tbl),
  compute_table3_row(hh_results,         hh_icatcher,         "Social Evaluation",                   14, Part_Age, show_away = TRUE,  quality_tbl = hh_quality_tbl)
)

table3 <- table3 %>% dplyr::select(Task, N_trials_QC, contains("valid"), contains("zero"), contains("noface"), contains("away"), contains("lowconf"))

colnames(table3) <- c(
  "Task",
  "N trials (QC)",
  paste0("N valid iCatcher+ (", age_levels, ")"),
  paste0("N 0% completion (", age_levels, ")"),
  paste0("Median (IQR) % no-face frames (", age_levels, ")"),
  paste0("Median (IQR) % away frames (", age_levels, ")"),
  paste0("Median (IQR) % low-confidence frames (", age_levels, ")")
)



table3 %>%
  knitr::kable(format = "html",
               caption = "Table 3: Data quality metrics from iCatcher+ output across all administered trials.") %>%
  kableExtra::kable_styling("striped", full_width = TRUE) 

# ------------------------------------------------------------------------------
# Build Table 4
# ------------------------------------------------------------------------------

table4 <- bind_rows(
  make_table4_row(GS_enrollment,        GS_results,         GS_icatcher,         "Geo-Social Attention",         10, Part_Age, "Trial"),
  make_table4_row(vpc_enrollment,        vpc_results,        vpc_icatcher,        "Visual Paired Comparison",      6, Part_Age, "Trial Total"),
  make_table4_row(Prediction_enrollment, Prediction_results, prediction_icatcher, "Prediction",                   14, Part_Age, "Trial",
                  final_df = prediction_final,
                  final_id_col = "response_uuid",
                  trials_per_person_override = prediction_final %>%
                    group_by(response_uuid) %>%
                    summarise(n_trials = sum(n2), Age = first(Age), .groups = "drop")),
  make_table4_row(AV_enrollment,         AV_results,         AV_icatcher,         "Audiovisual Synchrony",         6, Part_Age, "Trial"),
  make_table4_row(WL_enrollment,         WL_results,         WL_icatcher,         "Word Comprehension",            5, Part_Age, "Trial",
                  final_df = df_list_diff_enroll, final_trial_col = "Word_Pair"),
  make_table4_row(numeracy_enrollment,   numeracy_results,   Numeracy_icatcher,   "Numeracy",                      4, Part_Age, "Trial"),
  make_table4_row(hh_enrollment,         hh_results,         hh_icatcher,         "Social Evaluation",             2, Part_Age, "Trial Total")
)

table4 <- table4 %>% dplyr::select(Task, Analytic_trials, contains("valid"), contains("usable"), contains("sidebias"), contains("final"), contains("Med_trials"))


colnames(table4) <- c(
  "Task",
  "Analytic trials/word pairs",
  paste0("N valid iCatcher+ (", age_levels, ")"),
  paste0("N \u226533% usable frames (", age_levels, ")"),
  paste0("N side bias (", age_levels, ")"),
  paste0("N final analytic sample (", age_levels, ")"),
  paste0("Median (IQR) trials (", age_levels, ")")
)

table4 %>%
  knitr::kable(format = "html",
               caption = "Table 4: Participant retention across data quality and inclusion criteria steps, by task and age group.") %>%
  kableExtra::kable_styling("striped", full_width = TRUE) 

```

```{r final-list}
results_list <- list(
  list(label = "Geo-Social Attention",      tab = tab_geo),
  list(
    label       = "VPC",
    tab         = tab_vpc,
    stim_levels = c("Social", "Non-social"),      # must match what's in tab$Condition
    stim_labels = c("VPC Social (face)",
                    "VPC Non-social (fribbles)")
  ),
  list(
    label       = "Prediction",
    tab         = tab_pred,
    stim_levels = c("Block 1", "Block 2"),      # must match what's in tab$Condition
    stim_labels = c("Prediction Block 1",  # optional: custom Task column labels
                    "Prediction Block 2")
  ),
  list(label = "AV Synchrony",      tab = tab_av),
  list(label = "Word comprehension",      tab = tab_word),
  list(
    label       = "Numeracy",
    tab         = tab_num,
    stim_levels = c("Small Constant", "Large Constant"),      # must match what's in tab$Condition
    stim_labels = c("Numeracy 5-item stream constant",  # optional: custom Task column labels
                    "Numeracy 20-item stream constant")
  ),
  list(label = "Social Evaluation",      tab = tab_hh)
)


make_summary_table(results_list, age_levels = c("6", "12"))

```


```{r full}

# All models and files for the manuscript
tab_geo_full <- run_condition_model(
  data = GS_enrollment$metrics,
  condition_var = "Age",
  metric = "target_prop",
  chance_level = 0.5,
  random_effects = c("(1 | response_uuid)", "(1 | Trial)"),
  interaction = FALSE
)

tab_vpc_full <- run_condition_model(
  data = vpc_enrollment$metrics %>% 
    dplyr::rename(Stimulus_type = "Stimulus type"),
  condition_var = c("Age", "Stimulus_type"),
  metric = "target_prop",
  chance_level = 0.5,
  random_effects = c("(1 | response_uuid)", "(1 | `Trial Total`)"),
  interaction = TRUE
)

tab_pred_full <- run_condition_model(
  data = prediction_final,
  condition_var = c("Age", "block"),
  metric = "aem_prop",
  chance_level = 0.5,
  random_effects = c("(1 | response_uuid)"),
  interaction = TRUE
)

tab_av_full <- run_condition_model(
  data = AV_enrollment$metrics,
  condition_var = "Age",
  metric = "target_prop",
  chance_level = 0.5,
  random_effects = c("(1 | response_uuid)", "(1 | Trial)"),
  interaction = FALSE
)

tab_word_full <- run_condition_model(
  data = df_list_diff_enroll,
  condition_var = "Age",
  metric = "diff",
  chance_level = 0,
  random_effects = c("(1 | response_uuid)", "(1 | Word_Pair)"),
  interaction = FALSE
)

tab_num_full <- run_condition_model(
  data = df_numeracy_enrollment %>% 
    dplyr::rename(Stimulus_type = `Stimulus type`),
  condition_var = c("Age", "Stimulus_type"),
  metric = "target_prop",
  chance_level = 0.5,
  random_effects = c("(1 | response_uuid)", "(1 | Trial)"),
  interaction = TRUE
)

tab_hh_full <- run_condition_model(
  data = df_hh,
  condition_var = "Age",
  metric = "target_prop",
  chance_level = 0.5,
  random_effects = c("(1 | response_uuid)"),
  interaction = FALSE
)

tab_geo_full  <- tab_geo_full  %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)
tab_vpc_full  <- tab_vpc_full  %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)
tab_pred_full <- tab_pred_full %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)
tab_av_full   <- tab_av_full   %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)
tab_word_full <- tab_word_full %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)
tab_num_full  <- tab_num_full  %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)
tab_hh_full   <- tab_hh_full   %>% rename(estimate_ci = `Estimate (95% CI)`, p_value = `P-value`)

vpc_stim_by_age <- as.data.frame(
  emmeans(mod, pairwise ~ Stimulus_type | Age)$contrasts
)

make_table5_raw <- function(results_list, age_levels = c("6", "12")) {

  extract_non_interaction <- function(tab, label) {
    tibble::tibble(
      Task = label,
      Overall_Estimate = tab %>% filter(Condition == "Overall") %>% pull(estimate_ci),
      Overall_P = tab %>% filter(Condition == "Overall") %>% pull(p_value),
      Age_6_Estimate = tab %>% filter(Condition == "6") %>% pull(estimate_ci),
      Age_6_P = tab %>% filter(Condition == "6") %>% pull(p_value),
      Age_12_Estimate = tab %>% filter(Condition == "12") %>% pull(estimate_ci),
      Age_12_P = tab %>% filter(Condition == "12") %>% pull(p_value),
      Contrast_Estimate = tab %>% filter(Condition == "Age 12 - Age 6") %>% pull(estimate_ci),
      Contrast_P = tab %>% filter(Condition == "Age 12 - Age 6") %>% pull(p_value)
    )
  }

  extract_interaction <- function(tab, stim_levels, stim_labels) {
    purrr::map2_dfr(stim_levels, stim_labels, function(stim, label) {
      tibble::tibble(
        Task = label,
        Overall_Estimate = tab %>% filter(Condition == paste0(stim, " | Overall")) %>% pull(estimate_ci),
        Overall_P = tab %>% filter(Condition == paste0(stim, " | Overall")) %>% pull(p_value),
        Age_6_Estimate = tab %>% filter(Condition == paste0(stim, " | Age 6")) %>% pull(estimate_ci),
        Age_6_P = tab %>% filter(Condition == paste0(stim, " | Age 6")) %>% pull(p_value),
        Age_12_Estimate = tab %>% filter(Condition == paste0(stim, " | Age 12")) %>% pull(estimate_ci),
        Age_12_P = tab %>% filter(Condition == paste0(stim, " | Age 12")) %>% pull(p_value),
        Contrast_Estimate = tab %>% filter(Condition == paste0(stim, " | Age 12 - Age 6")) %>% pull(estimate_ci),
        Contrast_P = tab %>% filter(Condition == paste0(stim, " | Age 12 - Age 6")) %>% pull(p_value)
      )
    })
  }

  dplyr::bind_rows(
    extract_non_interaction(tab_geo_full, "Geo-Social Attention"),
    extract_interaction(
      tab_vpc_full,
      c("Social", "Non-social"),
      c("VPC Social (face)", "VPC Non-social (fribbles)")
    ),
    extract_interaction(
      tab_pred_full,
      c("Block 1", "Block 2"),
      c("Prediction Block 1", "Prediction Block 2")
    ),
    extract_non_interaction(tab_av_full, "AV Synchrony"),
    extract_non_interaction(tab_word_full, "Word Recognition"),
    extract_interaction(
      tab_num_full,
      c("Small Constant", "Large Constant"),
      c("Numeracy 5-item stream constant", "Numeracy 20-item stream constant")
    ),
    extract_non_interaction(tab_hh_full, "Social Evaluation")
  ) %>%
    dplyr::rename(
      `Estimate (95% CI)` = Overall_Estimate,
      `p` = Overall_P,
      `6 months Estimate (95% CI)` = Age_6_Estimate,
      `6 months p` = Age_6_P,
      `12 months Estimate (95% CI)` = Age_12_Estimate,
      `12 months p` = Age_12_P,
      `Age Effect Estimate (95% CI)` = Contrast_Estimate,
      `Age Effect p` = Contrast_P
    )
}

table5_df <- make_table5_raw()

figure3_rise <- cowplot::plot_grid(
  plot1_rise + theme(axis.title.y = element_text(size = 9)),
  plot4_rise + theme(axis.title.y = element_text(size = 9)),
  plot3_rise + theme(axis.title.y = element_text(size = 9)),
  plot2_rise + theme(axis.title.y = element_text(size = 9)),
  plot5_rise + theme(axis.title.y = element_text(size = 9)),
  plot6_rise + theme(axis.title.y = element_text(size = 9)),
  plot7_rise + theme(axis.title.y = element_text(size = 9)),
  NULL,
  ncol = 2,
  labels = c("a", "b", "c", "d", "e", "f", "g", ""),
  label_size = 10,
  rel_widths = c(1.15, 1.35),
  align = "none"
)

save(usable_frames_plot ,
  Part_Age,

  table3,
  table4,
  table5_df,
  
  task_usable,
  
  figure3_rise,
  prediction_aem_fig,

  tab_geo_full,
  tab_vpc_full,
  tab_pred_full,
  tab_av_full,
  tab_word_full,
  tab_num_full,
  tab_hh_full,

  vpc_stim_by_age,
  GS_enrollment,
  vpc_enrollment,
  Prediction_enrollment,
  AV_enrollment,
  WL_enrollment,
  numeracy_enrollment,
  hh_enrollment,

  df_numeracy_enrollment,
  prediction_final,
  df_list_diff_enroll,
  df_hh,

  file = here::here("Aim2", "Aim2_Computed_Data", "manuscript_objects.RData")
)

```


